---
title: ""
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Task : Prediction using Unsupervised ML

## Importing the Iris dataset
```{r}
myData <- read.csv("Iris.csv")
print(head(myData))
```

## Extracting features
```{r}
f <- c("SepalLengthCm","SepalWidthCm","PetalLengthCm","PetalWidthCm")
myFeatures = myData[f]
head(myFeatures)
```
## Analyzing the features
```{r}
summary(myFeatures)

```

## Importing ***ggplot(Grammar of Graphics)*** library for graph
```{r}
library(ggplot2)
```

## Plotting graph between PetalLengthCm and  PetalWidthCm
```{r}
ggplot(myData, aes(PetalLengthCm, PetalWidthCm)) + geom_point(aes(col=Species), size=4)
```

## Plotting graph between SepalLengthCm and  SepalWidthCm
```{r}
ggplot(myData, aes(SepalLengthCm, SepalWidthCm)) + geom_point(aes(col=Species), size=4)

```

## Finding optimal numbers of cluster
```{r}
twss <- vector(mode="character", length=10)
for (i in 1:10){
  clusters <- kmeans(myFeatures, center=i, nstart=20)
  twss[i] <- clusters$tot.withinss
}
plot(1:10, twss, type="b", pch=6)
```

> We can here clearly observe that *twss value* has significant decline between ***k = 2*** and ***k = 3***. Later, this decline in twss is not much.
> 
>Hence, we get the **optimal numbers of cluster = 3**


## Importing the Cluster Library for cluster plotting
```{r}
library(cluster)
```

## Plotting the clusters
```{r}
clusters <- kmeans(myFeatures, center=3, nstart=20)
clusplot(myFeatures, clusters$cluster, color=T, shade=T, labels=0, lines=0)
```

